Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-06-29 paper/arm.tex
a minor comment on PWT->Arm

\section{Lowering PwT-MCA to Arm}
\label{sec:arm}
For simplicity, we restrict to top level parallel composition and ignore
fences\footnote{Fences are not actions in \armeight{}, which complicates the
  theorem statements.}.

>>>>

\section{Lowering PwT-MCA to Arm}
\label{sec:arm}
For simplicity, we restrict to top level parallel composition and ignore
fences\footnote{Fences are not actions in \armeight{}, which complicates the
  theorem statements.%
  \app{Is it true? AFAIU, it isn't, they are explicitly used in definition of $\textsc{bob}$.
    I've just found that Jade prefers to omit them in pictures.}}.
